Stage-Splitting a Modal Language

### 2014-07-01 paper/semantics.tex
fix the issue with listings in footnotes

A function $f$ which accepts inputs at both stages \bbone{} and \bbtwo{} can be
given a type of the form $A\to\fut(B\to C)$%
\footnote{We can rewrite \texttt{fexp} in this form, or simply apply the following
higher-order function which makes the adjustment:

%\begin{lstlisting} 
%let adjust (f : $int * int -> $int) =
%	fn (p : int) => 
%		next{
%			fn (b : int) => 
%				prev{f (next {b}, p)}
%		}	
%\end{lstlisting}
\TODO code written, but listings don't work in footnotes! commented out in source until we get working
}.
Given its stage \bbone\ argument $a:A$, we can evaluate the partially-applied
function:
$\cdot;\cdot\vdash f~a \mathop{\redonesym} [\xi,v]$.
The result is an environment $\xi$ and a partial value $v$ of type $\fut(B\to
C)$. Next, we reify this environment into a sequence of \verb|let|-bindings
enclosing $v$, via $\reify\xi{v}{f_a}$. A canonical forms theorem on $v$
ensures that the resulting $f_a$ has type $B\to C$ in the residual language.
Finally, given a stage \bbtwo{} argument $b:B$, we can stage-\bbtwo{} evaluate
the ultimate result of the function, $f_a~b \mathop{\tworedsym} c$.

>>>>

A function $f$ which accepts inputs at both stages \bbone{} and \bbtwo{} can be
given a type of the form $A\to\fut(B\to C)$.%
\cprotect\footnote{We can rewrite \texttt{fexp} in this form, or simply apply
the following higher-order function which makes the adjustment:
\begin{lstlisting} 
let adjust (f : $int * int -> $int) =
  fn (p : int) => 
    next{
      fn (b : int) => 
        prev{f (next {b}, p)}
    }
\end{lstlisting}}
%
Given its stage \bbone\ argument $a:A$, we can evaluate the partially-applied
function:
$\cdot;\cdot\vdash f~a \mathop{\redonesym} [\xi,v]$.
The result is an environment $\xi$ and a partial value $v$ of type $\fut(B\to
C)$. Next, we reify this environment into a sequence of \verb|let|-bindings
enclosing $v$, via $\reify\xi{v}{f_a}$. A canonical forms theorem on $v$
ensures that the resulting $f_a$ has type $B\to C$ in the residual language.
Finally, given a stage \bbtwo{} argument $b:B$, we can stage-\bbtwo{} evaluate
the ultimate result of the function, $f_a~b \mathop{\tworedsym} c$.
